### 2021-06-06 paper/report.tex
Small updates.

        PCR tests: quarantine (?)

        Antigen tests: subsequent PCR tests, quarantine, work/school

        Effects on other people (tracing)

@@

        % \includegraphics[width=\textwidth]{../figures/model_detailed.png}
        \caption{{\small Model for translating simulated number to officially recorded cases}}
        \label{fig:model_for_official_cases}
    \end{subfigure}

@@

Figure~\ref{fig:pandemic_drivers_model_fit} describes the evolution of the pandemic and of its drivers. The black line in Figure~\ref{fig:aggregated_fit} shows officially recorded cases; the \replaced[id=HM]{color}{blue?} line in Figure~\ref{fig:stringency_index} the Oxford Response Stringency Index\cite{Hale2020}, which tracks the tightness of non-pharmaceutical interventions. We transform the index so that lower values represent higher levels of restrictions. A value of zero means all measures incorporated in the index are turned on. The value 1 represents the situation of mid-September, where half of all restrictions incorporated in the index are active.\comment[id=HM]{Need to find version of index with a couple of measures, probably need the API access...}. In the six weeks between mid September and mid October, cases increased by a factor of \replaced[id=HM]{X}{10? Do we have RKI numbers as table somewhere?}. Restrictions were somewhat tightened in mid-October and again in early November. New infections remained constant throughout November, before rising again in December. In mid December, other lockdown. So far, traditional measures only

Starting in January,  becomes relevant.
\begin{itemize}
    \item Vaccines
    \item Tests
    \item Seasonality March onwards.
    \item B.1.1.7 February onwards
\end{itemize}

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case}
        \caption{{\small Recorded cases: Empirical and simulated}}
        \label{fig:aggregated_fit}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/stringency}

        \textcolor{red}{Where to put seasonality?}
        \caption{{\small Contact reductions}}
        \label{fig:stringency_index}
    \end{subfigure}

@@

        \includegraphics[width=\textwidth]{../figures/results/figures/data/share_of_individuals_with_first_vaccine}

        \textcolor{red}{Number of PCR tests}

        \caption{{\small Tests and vaccinations}}
        \label{fig:pcr_antigen_tests_vaccinations}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/share_of_b117_acc_to_rki}

        \includegraphics[width=\textwidth]{../figures/results/figures/data/testing/assumed_overall_share_known_cases}

        \caption{Share of known cases and fraction of B.1.1.7 strain}
        \label{fig:share_known_cases_b117}
    \end{subfigure}

@@

@@

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
        \caption{{\small Recorded cases: 2021 scenarios}}
        \label{fig:full_new_known_case_cropped}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small Total cases: 2021 scenarios}}
        \label{fig:full_newly_infected_cropped}
    \end{subfigure}

@@

        \caption{
            Decomposition of effects for Figure~\ref{fig:full_newly_infected_cropped}.

            The decomposition is based on Shapley values where the individual
            contribution of an intervention is its average contribution over different
            sizes of coalitions (combinations with other interventions). The individual
            contribution to a coalition is the difference between the effect size of the
            coalition with the particular intervention and without.
        }
        \label{fig:decompisition total cases}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

@@

>>>>

@@

        \includegraphics[width=\textwidth]{../figures/model_detailed.png}
        \caption{{\small Model for translating simulated number to officially recorded cases}}
        \label{fig:model_for_official_cases}
    \end{subfigure}

@@

Figure~\ref{fig:pandemic_drivers_model_fit} describes the evolution of the pandemic and of its drivers. The black line in Figure~\ref{fig:aggregated_fit} shows officially recorded cases; the \replaced[id=HM]{color}{blue?} line in Figure~\ref{fig:stringency_index} the Oxford Response Stringency Index\cite{Hale2020}, which tracks the tightness of non-pharmaceutical interventions. We transform the index so that lower values represent higher levels of restrictions. A value of zero means all measures incorporated in the index are turned on. The value 1 represents the situation of mid-September, where half of all restrictions incorporated in the index are active.\comment[id=HM]{Need to find version of index with a couple of measures, probably need the API access...}. In the six weeks between mid September and mid October, cases increased by a factor of \replaced[id=HM]{X}{10? Do we have RKI numbers as table somewhere?}. Restrictions were somewhat tightened in mid-October and again in early November. New infections remained constant throughout November, before rising again in December.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case}
        \caption{{\small Recorded cases: Empirical and simulated}}
        \label{fig:aggregated_fit}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/stringency2}

        \caption{{\small Stringency of NPIs and changes in infectious contacts by type}}
        \label{fig:stringency_index}
    \end{subfigure}

@@

        \caption{{\small Tests and vaccinations}}
        \label{fig:antigen_tests_vaccinations}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/share_of_b117_acc_to_rki}

        \caption{Fraction of B.1.1.7 strain among measured infections}
        \label{fig:share_b117}
    \end{subfigure}

@@

    \floatfoot{
        Note: All aggregates; See S.XXX for statistics by age group and by geographical region. Also more disaggregated data.

        Sources: ... 
    }

@@

Quickly rising rates in December prompted the most stringent lockdown to this date. Schools and daycare centers were closed again, so were customer-facing businesses except for grocery and drug stores. Shortly afterwards, more factors become relevant. Just after Christmas, the first people were vaccinated with a focus on older age groups and medical personnel (Figure~\ref{fig:antigen_tests_vaccinations}. By the end of May, just over 40\% had received at least one dose of a vaccine. Starting in January, rapid tests \dots These had to be administered by medical doctors or in pharmacies. At-home tests approved by authorities were ... in March.\comment[id=HM]{update precise timeline}
From the peak of the second wave just before Christmas until the trough in mid-February, newly detected cases decreased by almost three quarters. The third wave in the spring of 2021 is associated with a rise in the share of the B.1.1.7 variant among all infections, depicted in Figure~\ref{fig:share_b117}, reaching more than 80\% in April\comment[id=HM]{Do we have the table somewhere?}. In early March, some NPIs were being relaxed; e.g., hairdressers and home improvement stores were allowed to open again to the public. In some cases, customers were only allowed to enter with a recent negative rapid test result.

The blue line in Figure~\ref{fig:aggregated_fit} shows the simulated infections based on our model.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
        \caption{{\small Recorded cases: 2021 scenarios}}
        \label{fig:full_new_known_case_cropped}
    \end{subfigure}
    %
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small Total cases: 2021 scenarios}}
        \label{fig:full_newly_infected_cropped}
    \end{subfigure}

@@

        \caption{Decomposition of effects for Figure~\ref{fig:full_newly_infected_cropped}.}

        \label{fig:decomposition_scenarios_total_cases}
    \end{subfigure}
    %
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

@@

    \floatfoot{
        Note: All aggregates; See S.XXX for statistics by age group and by geographical region.

        The decomposition is based on Shapley values where the individual contribution of an intervention is its average contribution over different sizes of coalitions (combinations with other interventions). The individual contribution to a coalition is the difference between the effect size of the coalition with the particular intervention and without.
    }
\end{figure}
